---
title: "Assignment 1"
output: html_notebook
---
## read and view data in R
```{r}
data = read.csv("mosqtemp.csv")
data

```

#### The first column is integer and last 5 columns are numerical.

#### The dimension of the dataset is  75x6. This means the dataset has 6 colums and 75 rows.



#### Selecting a column using square brackets 
```{r}
data[ , 'Temp' ]
```
#### Selecting a column using  logical statements

```{r}
data[ data$Temp > 11 , 'Temp']
```
```{r}
summary(data)
```
#### Summery of my data gives me a simple statistics of each column.The statistics includes Max, Median, Mean, Min, 1st Quartile and 3rd quartile of the colums.

#### Do a calculations with your data where you add a column 

```{r}
data$double_Urban = data$Urban * 2
data
```

```{r}
aggregate(Precip ~ SppRichness, data = data, FUN = mean)
```
```{r}
aggregate(Precip ~ SppRichness, data = data, FUN = sum)
```

```{r}
aggregate(Precip ~ SppRichness, data = data, FUN = max)
```
```{r}
aggregate(Precip ~ SppRichness, data = data, FUN = min)
```









































