---
title: "Assignment"
output:
  pdf_document: default
  html_notebook: default
---
## read and View data in R

```{r}
library(readr)
fish_data <- read_csv("fish_data.csv")
```

```{r}
View(fish_data)
print(fish_data)
```


#### The first, second and third, fifth, eighth columns are  numerical, fourth and sixth columns are character and seventh colum is logical

#### The dimension of the dataset is  2000x8. This means the dataset has 2000 rows and 8 columns



#### Selecting a column using square brackets

```{r}
fish_data[ , 'ph_of_water' ]
```
#### Selecting a column using  logical statements


```{r}
fish_data[ fish_data$ph_of_water > 7 , 'ph_of_water']
```

#### summary of data


```{r}
summary(fish_data)
```
#### Summery of this data gives a simple statistics of each column.The statistics includes Max, Median, Mean, Min, 1st Quartile and 3rd quartile of 1st, 2nd, 3rd, 5th, 8th colums; length, class, mode of 4th and 6th colums; mode, false true and  NA's of 7th colum.

#### Calculation of data with adding a column


```{r}
fish_data$double_ph_of_water = fish_data$ph_of_water * 2
head(fish_data)
```



#### Use base R to aggregate data

```{r}
aggregate(ph_of_water ~ habitat, data = fish_data, FUN = mean)
```


```{r}
aggregate( average_length ~ habitat, data = fish_data, FUN = mean)

```

```{r}
aggregate( average_length ~ habitat, data = fish_data, FUN = sum)

```

```{r}
aggregate( average_length ~ habitat, data = fish_data, FUN = max)
```

```{r}
aggregate( average_length ~ habitat, data = fish_data, FUN = min)
```






